Statically Typed String Sanitation Inside a Python

### 2014-08-18 sanitation-psp14/sanitation-psp14-short.tex
strcase

% Meta-theoretic functions
\newcommand{\lsubst}[3]{{\tt subst}(#1;#2;#3)} % This used to renderlreplace(...) so there're probably mistkes wherever this command was used now.
\newcommand{\lreplace}[3]{{\tt lreplace}(#1; #2; #3)}

@@

@@

@@

@@

@@

@@

>>>>

% Meta-theoretic functions
\newcommand{\lsubst}[3]{{\sf subst}(#1;#2;#3)} % This used to renderlreplace(...) so there're probably mistkes wherever this command was used now.
\newcommand{\lreplace}[3]{{\sf lreplace}(#1; #2; #3)}

\newcommand{\strcase}[3]{ {\sf strcase}(#1; #2; #3)}
\newcommand{\pstrcase}[3]{ {\sf pstrcase}(#1; #2; #3)}

\newcommand{\lhead}[1]{ {\sf lhead}(#1) }
\newcommand{\ltail}[1]{ {\sf ltail}(#1) }

@@

\begin{defn}[Definition of \lhead{r}]
The function $\lhead{r}$ is defined in terms of the structure of $r$:
\begin{itemize}
\item $\lhead{a r'} = a$ where $a \in \Sigma$
\item $\lhead{r_1 \cup  r_2}  = \lhead{r_1} \cup \lhead{r_2}$
\item $\lhead{r*} = \lhead{r}$
\item $\lhead{.} = a_1 \cup a_2 \cup ... \cup a_n$ for all $a_i \in \Sigma$ where $|\Sigma| = n$
\item $\lhead{\epsilon} = \epsilon$.
\end{itemize}
\end{defn}

\begin{defn}[Definition of \ltail{r}]
The function \ltail{r} is defined in terms of $\lhead{r}$.
Note that $\lhead{r} = a_1 \cup a_2 \cup ... \cup a_i$.
We define $\ltail{r} = \delta_{a_1}(r) \cup \delta_{a_2}(r) \cup ... \cup \delta_{a_i}(r)$
where $\delta_s(r)$ is the Brzozowski derivative of $r$ with respect to $s$ \cite{bowzer}.
\end{defn}

@@

\inferrule[S-T-Case]
{ \sctx \vdash e_1 : \stringin{r} \\
  \sctx \vdash e_2 : \sigma \\
  \sctx, x : \stringin{\lhead{r}}, y : \stringin{\ltail{r}} \vdash e_3 : \sigma
}
{
  \sctx \vdash \strcase{e_1}{e_2}{x.y.e_3} : \sigma
}

@@

\inferrule[S-E-Case-$\epsilon$]
{
  e_1 \sreduces \strin{\epsilon} \\
  e_2 \sreduces v_2
}
{
  \strcase{e_1}{e_2}{e_3} \sreduces v_2
}

\inferrule[S-E-Case-Concat]
{
  e_1 \sreduces \strin{p s} \\
  e_3 \sreduces x.y.e_4 \\
  [p/x][s/y]e_4 \sreduces v
}
{
  \strcase{e_1}{e_2}{e_3} \sreduces v
}

@@

\inferrule[P-T-Case]
{\tctx \vdash \iota_1 : \str \\ \tctx \vdash \iota_2 : \tau \\ \tctx, x:\str, y:\str \vdash \iota_3:\tau}
{\tctx \vdash \pstrcase{\iota_1}{\iota_2}{\iota_3} : \tau}

@@

\inferrule[P-E-Case-$\epsilon$]
{
  \iota_1 \treduces \tstr{\ } \\
  \iota2 \treduces \iota_2
}
{
  \pstrcase{\iota_1}{\iota_2}{\iota_3} \treduces v_2
}

\inferrule[P-E-Case-Concat]
{
  \iota_1 \treduces \tstr{ps} \\
  x.y.\iota_3 \treduces \iota_4 \\
  [p/x][s/y]\iota_4 \treduces v
}
{
  \pstrcase{\iota_1}{\iota_2}{\iota_3} \treduces v
}

@@

\inferrule[Tr-Case]
{\sctx \vdash \trden{e_1} = \iota_1 \\
  \sctx \vdash \trden{e_2} = \iota_2 \\
  \sctx \vdash \trden{e_3} = \iota_3
}
{\sctx \vdash \trden{ \strcase{e_1}{e_2}{e_3} } = \pstrcase{\iota_1}{\iota_2}{\iota_3} }
